Efficient Community Formation \\ for Web Services

### 2013-12-21 papers/coalition-journal-R1/coalition_journal_r1.tex
changes

The need for highly available and responsive services has called
for grouping and collaborative mechanisms of loosely-coupled web
services, particularly in business settings
\cite{YuB13,Younas2012,LiuBWZ13}. The idea of grouping web
services within communities and the way those communities are
engineered so that web services can better collaborate have been
proposed and investigated in
\cite{DBLP:journals/ijebr/MaamarSTBB09,DBLP:journals/internet/BenatallahSD03,Rosario:2008:PQS:1512146.1512290}.
Communities are virtual groups of web services having similar or
complementary functionalities \cite{Zeng:2003:QDW:775152.775211,
Paik:2005:TSS:2229263.2230038,Medjahed05adynamic,10.1109/ARES.2008.7},
but probably different non-functional quality attributes, which
form the QoS parameters. When communities are used, users send
their requests to the masters of those communities, which are
responsible of managing the communities, forwarding the requests
to the suitable member web services and checking the credentials
of those members. Communities aim to provide higher service
availability and performance than what individual web services can
do. The high availability of services and the community resilience
to failure are guaranteed since web services can cooperate and
replace each other within the same community and since there is no
single point of failure in the communities architecture.

>>>>

The need for highly available and responsive services has called
for grouping and collaborative mechanisms of loosely-coupled web
services, particularly in business settings
\cite{YuB13,Younas2012,LiuBWZ13}. The idea of grouping web
services within communities and the way those communities are
engineered so that web services can better collaborate have been
proposed and investigated in
\cite{DBLP:journals/ijebr/MaamarSTBB09,DBLP:journals/internet/BenatallahSD03,Rosario:2008:PQS:1512146.1512290}.
Communities are virtual groups of web services having similar or
complementary functionalities \cite{Zeng:2003:QDW:775152.775211,
Paik:2005:TSS:2229263.2230038,Medjahed05adynamic,10.1109/ARES.2008.7},
but probably different non-functional quality attributes, which
form the QoS parameters. When communities are used, users send
their requests to the coordinators of those communities, which are
responsible of managing the communities, forwarding the requests
to the suitable member web services and checking the credentials
of those members. Communities aim to provide higher service
availability and performance than what individual web services can
do. The high availability of services and the community resilience
to failure are guaranteed since web services can cooperate and
replace each other within the same community and since there is no
single point of failure in the communities architecture.
